### 2017-01-27 thesis/latex/thesis.tex
table written while meeting with Elliott

\begin{figure}[h]
  \centering
  \includegraphics[width=.85\textwidth,keepaspectratio]{../../figures/mechanochemical-cycle.jpeg}
  \caption{Cycle of states the dynein motor goes through during motion in the Cianfrocco model \cite{cianfroccoreview}.}
  \label{mech-cycle}
\end{figure}

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[width=.85\textwidth,keepaspectratio]{../../figures/mechanochemical-cycle.jpeg}
  \newcommand\bothbound{\textcolor{blue}{BOTHBOUND}}
  \newcommand\onebound{\textcolor{red}{ONEBOUND}}
  \newcommand\transition{\textcolor{green}{transition?}}
  \begin{tabular}{rll}
    \bothbound &
    1 & \begin{minipage}{5in}
      Bound to microtubule and waiting for ATP to arrive.  The
      conformation is ``post-powerstroke''.
    \end{minipage}\vspace{0.5em}\\
    \bothbound &
    2 & \begin{minipage}{5in}
      ATP has bound to the motor at AAA1, but nothing else has changed.
    \end{minipage}\vspace{0.5em}\\
    \transition &
    3 & \begin{minipage}{5in}
      ``The ring has closed'' in the motor, whatever that means.
    \end{minipage}\vspace{0.5em}\\
    \bothbound &
    4 & \begin{minipage}{5in}
      The affinity to the microtubule is dropped, so it is likely to pop off soon.
    \end{minipage}\vspace{0.5em}\\
    \onebound &
    5 & \begin{minipage}{5in} It has popped off of the microtubule!
      Onebound! The equilibrium angle is also changed.  The ATP has
      been hydrolized, but the phosphate is still bound to the motor.
      ``Priming stroke?''
    \end{minipage}\vspace{0.5em}\\
    \onebound &
    6 & \begin{minipage}{5in} It is now bound to the microtubule, but
      with low affinity, and without any loss of phosphate. Question:
      does this happen many times? If so it may still be onebound.
      Otherwise it is probably bothbound.
    \end{minipage}\vspace{0.5em}\\
    \bothbound &
    7 & \begin{minipage}{5in}
      Now it is seriously bound to the microtubule, and the motor
      domain has changed conformation.  This is now ``high affinity.''
    \end{minipage}\vspace{0.5em}\\
    \bothbound &
    8 & \begin{minipage}{5in}
      Phosphate has been released, and our equilibrium angles have
      been changed.  This is the ``power stroke.''
    \end{minipage}\vspace{0.5em}\\
    \bothbound &
    1 & \begin{minipage}{5in}
      The ADP has been released from the motor domain, so it can now
      bind ATP.  Still ``high affinity,'' and still in the
      ``power-stroke'' conformation.
    \end{minipage}\vspace{0.5em}\\
    \bothbound &
    9 & \begin{minipage}{5in}
      While stuck in this ``normal bound'' state, another site on the
      motor AAA3 can lose its ADP, which leaves the motor in a state
      where it cannot directly move on to step 2 (until after
      reversing this).  Controversial?
    \end{minipage}
  \end{tabular}
  \caption{Cycle of states the dynein motor goes through during motion in the Cianfrocco model \cite{cianfroccoreview}.}
  \label{mech-cycle}
\end{figure}
